ZCB Pricing

### 2018-07-02 ZCB Pricing .Rmd
I have uploaded aother verion og the MOnte Carlo simulations which makes use of the Euler discretization.
The Variance reduction methods have also been uploaded

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls(all =TRUE))
```

@@

```{r}
#Generate normal RV
z=rnorm(1000)
z.=-z

# Another Version of the MOnte Carlo simulations
Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int.=exp(-Sum.)
  int=exp(-Sum)# Estimate using the conjugate rates
  Average=(int+int.)/2 # Average of estimates
  mean=mean(Average)
  sd=sd(Average)/sqrt(n)
  result=c(mean,sd)
  result

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(s)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

@@

Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}

@@

explicit <- function(alpha,beta,sigma,r,I){

# I = partition of time
# J = partition of rate
# dr = length of rate sub-intervals
# r must be in the middle of partition of J
# length of J must be twice the length of I
dr <- 2*r/(2*length(I))

J <- seq(0,2*r,dr)

dt = 1/length(I) # length of each time sub-interval

V <- matrix(NA, nrow = length(J), ncol = length(I)+1) # empty matrix
nr <- length(J) # number of rows of the matrix - represents partition of rate
nt <- length(I)+1 # number of columns - represents partition of time

V[,length(I)+1] <- rep(1) # Boundary condition at expiry of bond

count <- 0 # set up count variable
for (i in rev(I)){ # rev is the reverse order of the time partition
  count <- count+1 # keeping track of loop
  for (j in (1+count):(nr-count)){
    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
    pm <- 1/dt -sigma^2/(dr^2) # middle value
    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
  }

V[(nr+1)/2,1]
}

explicit(0.01,0.1,0.04,0.05,1:10)

@@

```{r 5}
# Implicit Method

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
# Another version of the MOnte Carlo simulation

#Generate normal RV
z=rnorm(1000)
z.=-z

Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]# Makes use of conjugate estimates
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int.=exp(-Sum.)
  int=exp(-Sum)
  Average=(int+int.)/2 # Average of both vectors
  mean=mean(Average)
  sd=sd(Average)/sqrt(n)
  result=c(mean,sd)
  result

}
```

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(s)
  z_m= z-mean(z)  # Moment matching transformation

@@

Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}
```

@@

explicit <- function(alpha, beta, sigma, T, r, j, s){

# j = number of sub-intervals for the short rate
# s = number of sub-intervals for the time interval

dr = 1/j # lenght of short rate intervals
dt = T/s # lenght of time intervals

p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
p_m <- 1/dt -(sigma^2)/(dr^2)
p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)

V <- matrix(NA, nrow = j + 1, ncol = s + 1)
V[,s+1] <- rep(1)
V[j+1,] <- rep(1)
for (n in seq(s,0,-1)){
    for (i in 1:j)
       if (i == 1)
         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
       else
         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])

}
V
}

@@

```{r 5}
# Implicit Method
```
